Apples and Oranges in Adolescent Depression Treatments.

### 2024-01-03 apples_and_oranges.qmd
Fixed error causing distinct active conditions to be excluded

# Step 2: turn dataframes to long
# A: turn long the rows with active
turn_long_active_type <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, active_type, psy_or_med, baseline_n_active, cohens_d_active) %>% 
  pivot_longer(cols = c(cohens_d_active), 
               names_to = "arm_effect_size", 
               values_to = "cohens_d")

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type,treatment = active_type,
                                baseline_n = baseline_n_active)

>>>>

# Step 2: turn dataframes to long
# A: turn long the rows with active
turn_long_active_type <- df_with_distinct_instruments %>% 
  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active) %>% 
  pivot_longer(cols = c(cohens_d_active), 
               names_to = "arm_effect_size", 
               values_to = "cohens_d")

# also rename active_type to treatment for the merge below.
turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
                                baseline_n = baseline_n_active)
